\section{Additional Experience}

\cventry{aug 2015 \\ to may 2016}{Resident Advisor}{Rochester Institute of Technology}{Rochester, NY}{}{Resident advisor at the residence halls at the institute.
\begin{itemize}
    \item Advised 26 residents in the residence halls, assisted and supported residents with personal and interpersonal issues, directed residents to resources on campus and encouraged resident engagement, inclusion, student success and wellness.
    \item Collaborated with other Resident Advisors on community development events, developed floor programs to promote a sense of community.
\end{itemize}}

\cventry{summer 2012}{Library Intern}{Weil, Gotshal \& Manges}{New York, NY}{}{Intern at the law library at the law firm.
\begin{itemize}
    \item Developed a JavaScript-based slideshow application for the firm’s internal portal website.
    \item Conducted legal research for attorneys and staff at the firm.
    \item Wrote legal memorandums and performed document review.
\end{itemize}}

\cventry{oct 2012 \\ to dec 2013}{Administrative Assistant}{Gastroenterology Associates}{Garden City, NY}{}{Administrative assistant at the gastroenterology practice.
\begin{itemize}
    \item Scanned patient charts into the electronic health records system.
\end{itemize}}

\cventry{nov 2011 \\ to oct 2012}{Administrative Assistant}{Country Foot Care}{Mineola, NY}{}{Administrative assistant at the podiatric practice.
\begin{itemize}
    \item Scanned patient charts into the electronic health records system.
    \item Enabled the office to complete transition into a paperless office.
\end{itemize}}
