\section{Experience}
\cventry{aug 2015 \\ to may 2016}{Resident Advisor}{Rochester Institute of Technology}{Rochester, NY}{}{Resident advisor at the residence halls at the institute.
\begin{itemize}
\item Advised 26 residents in the residence halls, assisted and supported residents with personal and interpersonal issues, directed residents to resources on campus and encouraged resident engagement, inclusion, student success and wellness.
\item Collaborated with other Resident Advisors on community development events, developed floor programs to promote a sense of community.
\end{itemize}}
\cventry{jan 2015 \\ to jul 2015}{Software Engineer Co-op}{EagleDream Technologies}{Rochester, NY}{}{Worked with a team developing the EagleDream Health medical records analysis web application.
\begin{itemize}
\item Developed a module to extract, transform and load data from existing electronic health record systems into database for analysis using Java and Amazon Web Services.
\item Worked on the middle and front end of an electronic records analytics web application based on Java, Spring and AngularJS
\end{itemize}}
\cventry{summer 2014}{Undergraduate Research Assistant}{Rochester Institute of Technology}{Rochester, NY}{}{Worked as a research assistant to a professor researching accessible technologies for the deaf.
\begin{itemize}
\item Researched methods of improving accessibility to deaf students in the classroom using technology.
\item Developed a prototype browser-based captioning system for the classroom using JavaScript, Python, Node.js and Socket.io.
\end{itemize}}
\cventry{spring 2013}{Undergraduate Research Assistant}{Nassau Community College}{Garden City, NY}{}{Worked with students and faculty on the MouseTrap project with the GNOME Accessibility Team.
\begin{itemize}
\item Analyzed and inspected existing Python code, which had few comments and almost no documentation, and wrote documentation and software requirements specifications.
\end{itemize}}
